### 2023-06-02 paper.tex
new version

@@

@@

    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{images/14-bis.jpeg}

@@

      \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/nimbodetector.png}	

@@

      \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{images/sensor.png}	

@@

    \includegraphics[width=0.85\textwidth, trim={0 0 0 0},clip]{images/graph.png}

@@

\theauthorcontributions

>>>>

% https://www.dropbox.com/scl/fo/mvds2vmlka4j33v69ip6r/h?dl=0&rlkey=osfeagghu2lh4qkr5ig9w0v47
% https://www.dropbox.com/scl/fo/on0xgqzaeds3ys9b2sxxy/h?dl=0&rlkey=xvgm1v2arob7lzi7lvggmea81

@@

%\addextraspaceoncoverpage{25mm}

@@

    \includegraphics[width=0.55\textwidth, trim={0 0 0 0},clip]{author_files/14-bis.jpeg}

@@

      \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{author_files/nimbodetector.png}	

@@

      \includegraphics[width = \textwidth, trim={0 0.8cm 0 0.9cm},clip]{author_files/sensor.png}	

@@

    \includegraphics[width=0.85\textwidth, trim={0 0 0 0},clip]{author_files/graph.png}

@@

\theauthorcontributions{authorshipAndContributions.tex}
